Fully Extrinsic Type Inference (DRAFT 2025-06-17)

### 2025-07-17 doc/extrinsic_type_inference_paper/paper.tex
update stream and diff examples
update notes on title and how recursive types fit in

\title{Extrinsic Type Inference (DRAFT 2025-06-09)}
\author{Thomas Logan}

@@

\TODO{
I think the main novelty of my type inference design beyond previous systems is that it can infer recursive types extrinsically and then reason inductively with those types. Do you think that the title should reflect that?
}
\TODO{
e.g. “Extrinsic Reconstruction of Recursive Types”
}
\TODO{
e.g. “Inductive Subtyping over Reconstructed Recursive Types”
}

\TODO{don't need to call out extrinsic, because recursive types are the final hurdle in type inference}

@@

\examp{
  \J{def repeat = [x => loop([self => [n =>}
  \\
  \I\J{n |> [}
  \\
  \I\I \J{[zero;\_ => nil;(n.zero)]}
  \\
  \I\I \J{[succ;\_ => cons;(x,self(n.succ))]}
  \\
  \I \J{]}
  \\
  \J{])]}
}

@@

@@

>>>>

\title{Fully Extrinsic Type Inference (DRAFT 2025-06-17)}
\author{Thomas Logan}

@@

\TODO{Mention how reconstruction of recursive types is the last hurdle to fully extrinsic types}

@@

\examp{
  \J{def repeat = [x => loop([self => [n =>}
  \\
  \I\J{n |> [}
  \\
  \I\I \J{[zero;\_ => nil;(n.zero)]}
  \\
  \I\I \J{[succ;\_ => cons;(x,self(n.succ))]}
  \\
  \I \J{]}
  \\
  \J{]])]}
}

@@

\examp{
  \J{loop([self => [x =>}
  \\
  \I\J{[@ => (x, self(succ;x))]}
  \\
  \J{]]}
}

\examp{
  \J{ALL[T] T -> @ ->}
  \\
  \I\J{LFP[U] (LFP[R] T | <succ> R) * (@ -> U)}
}

% (ALL[G009] (G009 -> (LFP[G007] (EXI[G010] (G010 <: G007)  : (@ -> ((LFP[G007] (<succ> G007 | G009)) * G010))))))

@@

\examp{
  \J{LFP[R] (<zero> @) | (<succ> <succ> R)}
  \\
  \subtypes
  \\
  \J{TOP\typdiff (<succ> <succ> <succ> <zero> @)}
}
